---
title: "Dedupe Resource List"
output: html_notebook
---

```{r libraries, include=FALSE}
library(tidyverse)
```


Listing of paths for where Rstudio can find certain resources.
```{r}
#Starting Resources
resources_path <- "data/MasterList-Agency-Finder.csv"

covid_resources_path<- "data/ResourcesCOVID.csv"


# Resources created in deduplication process

comb_res_path <- "data/comb_res.csv" # this resource is created in Step 3 of Preparation






# resources from dedupe.io
program_clusters_path <-"data/Org Resource List.csv"  # programs with cluster program ID


```



# Purpose 
Dedupe Resource Lists for Covid and resource directory.

The plan is to first dedupe the Organization names and program names. 



# Preparation Work before deduplication

### Step 1: Open Refine Cleanup

Ran both lists of data "Master-Agency-Finder" and "ResourcesCovid" though OpenRefine and corrected Standardize Org names with the cluster feature.


### Step 2: Pulled lists of cleaned resources into Rstudio 




Importing of resources into RStudio
```{r Import data, include=FALSE}
#import datas into Rstudio

#resources sheet
resources <- read_csv(resources_path)

#Covid resources
covid_res <- read_csv(covid_resources_path)
```



Rename columns in our dataframe to make them easier to work with.

```{r}
resources <- resources %>% 
  rename('MSheetID' = 'Column','Org' = 'Organization Name', 'Program' = 'Program Name', 'Street' = 'Street Address') %>% 
  mutate(Zip = str_remove(Zip, "\\.0")) # removes the unnecessary ".0" from zip code


covid_res <- covid_res %>% 
  rename('Org' = 'Org', 'Program' = 'Program Name','Street' ='Street Address')
```




### Step 3: Creating a Single Resources dataframe

Combine two sheets into one dataframe for preparation in the deduplication process.

Shorten dataframes into only the necessary columns for the deduplication 


Which columns do we want to keep from each dataframe?
```{r}
# Define variables of columns to use in the dedupe process
resources_columns_keep <- c('MSheetID', 'Org', 'Program', 'Street', 'City', 'Zip')


covid_res_columns_keep <- c('CSheetID',  'Org', 'Program', 'Street', 'City', 'Zip' )
```



```{r}
#create  resources dataframe with columns selected
resources.df <- select(resources,
                       resources_columns_keep
                       )

# create covid dataframe with columns selected
covid_res.df <- select(covid_res, 
                       covid_res_columns_keep
                       )
```






Create a combined resources dataframe by appending the rows of resources.df to the rows of covid_res.df


First, you need to make sure all columns have the same name.

```{r}
#test whether column names are exactly the same
colnames(resources.df) == colnames(covid_res.df)


colnames(resources.df)

colnames(covid_res.df)


```


Need to remain the ID column to just a generic 'ID' for both.

```{r}
#renaming to generic ID column
resources.df<- rename(resources.df, 'ID' = 'MSheetID')

covid_res.df<- rename(covid_res.df, 'ID' = 'CSheetID')

```


Check colnames again
```{r}
#test whether column names are exactly the same
colnames(resources.df) == colnames(covid_res.df)


colnames(resources.df)

colnames(covid_res.df)
```

Since column names are the same we can append rows of resources to covid resources

```{r}
# creating combined resources dataframe by appending rows
comb_res <- bind_rows( covid_res.df, resources.df)
```



Step 3: Export this combined resource dataframe 

export file out
```{r}
write_csv(comb_res, comb_res_path)
```


# Deduplication Process

### Step 1: Create Clustering IDs

The deduplication process uses machine learning to help us create Ids of clusters for each Program and Organization. 

For this project this process was accomplished by using dedupe.io which has a offers the first 1,000 rows for free. Due to the time constraints we use this offer to dramatically spead up this process for creating clustering IDs.




## Use Clustering IDs to create tables needed in Database design


### Step 2: Import data from clustering process into Rstudio 
import clusters from dedupe Step

```{r}
program_clusters <- read_csv(program_clusters_path)
```



### Step 3: Add program clustering Ids to dataframes


```{r}
# create df's to store new tables with clustering IDs

resources.clustered <- resources

covid_res.clustered <- covid_res

```



Create joining table
```{r}
cluster_join <- select(program_clusters,
                       #fields
                       cluster_id, 
                       id)
```




Use left joins to add the program cluster ID to organizations to tables we just created.
```{r}
# Perform tasks for resources dataframe
resources.clustered <- left_join(resources.clustered, cluster_join, by= c('MSheetID'= 'id'))

#relocate joined cluster column to position 2
resources.clustered <- resources.clustered %>% 
  relocate(cluster_id, .after = MSheetID)


# Perform tasks for covid dataframe
covid_res.clustered<- left_join(covid_res.clustered, cluster_join, by = c("CSheetID"='id'))


# relocate cluster id column to position 2
covid_res.clustered <- covid_res.clustered %>% 
  relocate(cluster_id, .after = CSheetID)

```



### Step 4: Add the Unique Covid Programs to resources list


Create dataframes of the unique program cluster ids in resources and covid dataframes

```{r}
covid.unique<- as_tibble(  unique(covid_res.clustered$cluster_id))

resources.unique <- as_tibble(unique(resources.clustered$cluster_id))
```


These dataframes allow us to identify clusterIds present in one dataframe but not the other.
```{r}
#Covid program cluster IDs not matched to a resource program dataframe
covid_res_clusterid_not_matched <- anti_join(covid.unique, resources.unique)



# resources program cluster IDs not matched to the covid program dataframes
resources_clusterid_not_matched <- anti_join(resources.unique, covid.unique)

```


Filter to create data frame of covid resources not present in resources list.
```{r}
covid_res_unique <-filter(covid_res.clustered, 
                          #by
                          cluster_id %in% covid_res_clusterid_not_matched$value)
```



Create dataframe of covid resources which will be added to the resources list
```{r}
programs_add <-filter(covid_res_unique, 
                      #by where org is not Guilford County Schools
                      Org != 'Guilford County Schools')
```


```{r}
nrow(programs_add)
```


Will add `r nrow(programs_add)` programs from Covid resource list to master resource list.


### Step 5 create master resource list

```{r}
# subset of resources list
resource.comb <- select(
  resources.clustered,
  cluster_id,
  'Program Name',
  'Organization Name'
  
)

resource.comb <- rename(resource.comb, 'Org' ='Organization Name')

```



```{r}
covid.comb <- select(
  covid_res.clustered,
  cluster_id,
  'Program Name',
  Org
)
```


```{r}
#filter covid.comb to just the programs to add
covid.comb.add <-filter(
  covid.comb,
  cluster_id %in% programs_add$cluster_id
)

```






```{r}
# combine sublist together
Master_Resource_List <- bind_rows(resource.comb, covid.comb.add)
```


Function to add all appearances.
```{r}
appearances_list<- function(clustId){
  clusters = cluster_join
  
  clusters<- clusters %>% 
    filter( cluster_id==clustId)
  
  a = as.vector(clusters$id)
  
  
 return( paste0(a, collapse = ";  "))
  
}

appearances_list_vector <- Vectorize(appearances_list)
```


sanity check
```{r}
test.clusters<-count(cluster_join, cluster_id)

test2 <- filter(cluster_join, cluster_id =='ae0abbbc-a00d-4d21-ac6a-73764881e9b8')

```



```{r}
appearances_list('ae0abbbc-a00d-4d21-ac6a-73764881e9b8')
```
Passed sanity check



```{r}
#combine apperances in master list
Master_Resource_List<- Master_Resource_List %>% 
  mutate(sources = appearances_list_vector(cluster_id))

```



```{r}
#remove duplicates and grad first instance only
Master_Resource_List <- Master_Resource_List %>% 
  group_by(cluster_id) %>% 
  summarise(Progam = first(`Program Name`),
            Org = first(Org),
            sources= first(sources))
```



```{r}
# count the number of sources

Master_Resource_List <-Master_Resource_List %>% 
  mutate(n_sources= str_count(sources,';') + 1) %>%  # total number of sources
  mutate(M_n_sources = str_count(sources, 'M')) %>%  # num of sources from resources
  mutate(C_n_sources = str_count(sources,'C'))      # num of sources from covid list   

```



```{r}
Master_Resource_List.test<- Master_Resource_List %>% 
  filter(n_sources==2)
```


Add addresses to programs to aide in Org dedupe

Create a subset of resources with just the address fields we need

```{r}

resources.Addresses <- resources.clustered %>% 
  select(MSheetID, cluster_id, `Street Address`, City, Zip)
```

Ensure only one cluster in the resources.
```{r}
Remove_values <- Master_Resource_List %>% 
  filter(M_n_sources>1)

Remove_values<- Remove_values$cluster_id
```

```{r}
resources.Addresses <- resources.Addresses %>% 
  filter(!cluster_id %in% Remove_values)
```




left join of the data sets with Master_List


```{r}
Master_Resource_List <- left_join(Master_Resource_List, resources.Addresses, by= "cluster_id")
```





Rename cluster_id because we will run this though a second dedupe

```{r}
Master_Resource_List <- Master_Resource_List %>% 
  rename('cluster_id_program' = 'cluster_id')
```














Creat list of Orgs from Master List

```{r}
#write_csv(Master_Resource_List, "data/Master_Resource_list.csv")
```



import Orgs clustered
```{r}
Org_master_list <- read_csv('data/Org_Master_List_Clustered.csv')


Org_master_list<- Org_master_list %>% 
  rename('cluster_id_Org'='cluster_id')
```


Dedupe Org List

```{r}
Org_master_list.Dedupe <- Org_master_list %>% 
  group_by(cluster_id_Org) %>% 
  summarise(Org= first(org),
            street_address=first(street_address),
            city= first(city),
            zip = first(zip),
            n_sources= first(n_sources))

```

```{r}
na_Org_addresses<- Org_master_list.Dedupe %>% 
  filter(is.na(street_address))
```


```{r}
#write table for master list

#write_csv(Org_master_list, 'data/org_master_list.csv')
```



Create Program List
```{r}
program_list <- resource.comb %>% 
  rename(cluster_id_program = cluster_id) %>% 
  group_by(cluster_id_program) %>% 
  summarise(cluster_id_program = first(cluster_id_program),
            Program_Name = first(`Program Name`))
```

```{r}
program_list.test <- left_join(program_list, Master_Resource_List, by = "cluster_id_program")

```


```{r}
Org_master_list.comb <- select(Org_master_list,
                               cluster_id_program,
                               cluster_id_Org,)



program_list.test2 <- left_join(program_list.test, Org_master_list.comb, by = "cluster_id_program")
```

Combine from Agency Finder
```{r}
MasterList_Agency_Finder <- read_csv("data/MasterList-Agency-Finder.csv")
```


```{r}
program_list.test3 <- left_join(program_list.test2, MasterList_Agency_Finder, by= c('MSheetID'= 'Column'))
```



```{r}
write_csv(Org_master_list.Dedupe, 'data/orgl_list_upload.csv')

write_csv(program_list.test3, 'data/program_list.csv')
```




